---
title: "OT_vs_LIT"
output:
  html_document:
    toc: true
    toc_float: true
    theme: cerulean
    highlight: kate
    fig_width: 9
    fig_height : 7
    df_print: paged
    number_sections: true
---

```{r, include = FALSE}
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```

# Load packages

```{r}
library("tidyverse")
library("UpSetR")
library("patchwork")
library("ggpubr")
```

# Upset plot analysis

## Load files

```{r, echo = FALSE}
path <- ("C://Users/samgr/OneDrive - UCL/Documents/Internship/")
```


```{r}
DDA_1 <- read_tsv(paste0(path, "DDA_1ng.txt"))
DDA_5 <- read_tsv(paste0(path, "DDA_5ng.txt"))
DDA_10 <- read_tsv(paste0(path, "DDA_10ng.txt"))
DDA_100 <- read_tsv(paste0(path, "DDA_100ng.txt"))

DIA_1 <- 
  read.csv2(paste0(path, "20220420_142723_1ng_40SPD_LIT_turbo_8ms_1CV_Report.csv"))
DIA_5 <- 
  read.csv2(paste0(path, "20220420_142943_5ng_LIT_turbo_8ms_Report.csv"))
DIA_10 <- 
  read.csv2(paste0(path, "20220420_142500_CV-Turbo-8ms-LIT-10ng_Report.csv"))
DIA_100 <- 
  read.csv2(paste0(path, "20220420_143815_40SPD_whisper100_LITDIA_Turbo_8ms_1cv_100ng_Report.csv"))

```

## Filtering

### Filter potential contaminants and reverse

DDA 1ng
```{r}
dim(DDA_1)[1]
temp <- DDA_1 %>% 
  filter(is.na(DDA_1$Reverse))
DDA_1 <- temp %>% filter(is.na(temp$`Potential contaminant`))
dim(DDA_1)[1]
```

DDA 5ng
```{r}
dim(DDA_5)[1]
temp <- DDA_5 %>% 
  filter(is.na(DDA_5$Reverse))
DDA_5 <- temp %>% filter(is.na(temp$`Potential contaminant`))
dim(DDA_5)[1]
```

DDA 10ng
```{r}
dim(DDA_10)[1]
temp <- DDA_10 %>% 
  filter(is.na(DDA_10$Reverse))
DDA_10 <- temp %>% filter(is.na(temp$`Potential contaminant`))
dim(DDA_10)[1]
```

DDA 100ng
```{r}
dim(DDA_100)[1]
temp <- DDA_100 %>% 
  filter(is.na(DDA_100$Reverse))
DDA_100 <- temp %>% filter(is.na(temp$`Potential contaminant`))
dim(DDA_100)[1]
```

### Keep peptides found in 2 of the 4 replicates

#### Extract peptide sequences found in specific replicate


DDA 1ng
```{r}
table(DDA_1$`Raw file`)

DDA_1_1_pep <- DDA_1 %>% 
  filter(`Raw file` ==
           "20220414_HB_Evo_Whisper100_40SPD_LITDDA_HeLa_1ng_Turbo_1CV_8ms_S01") %>% 
  pull(Sequence)

DDA_1_2_pep <- DDA_1 %>% 
  filter(`Raw file` ==
           "20220414_HB_Evo_Whisper100_40SPD_LITDDA_HeLa_1ng_Turbo_1CV_8ms_S02") %>% 
  pull(Sequence)

DDA_1_3_pep <- DDA_1 %>% 
  filter(`Raw file` ==
           "20220414_HB_Evo_Whisper100_40SPD_LITDDA_HeLa_1ng_Turbo_1CV_8ms_S03") %>% 
  pull(Sequence)

DDA_1_4_pep <- DDA_1 %>% 
  filter(`Raw file` ==
           "20220414_HB_Evo_Whisper100_40SPD_LITDDA_HeLa_1ng_Turbo_1CV_8ms_S04") %>% 
  pull(Sequence)
```


DDA 5ng
```{r}
table(DDA_5$`Raw file`)

DDA_5_1_pep <- DDA_5 %>% 
  filter(`Raw file` ==
           "20220414_HB_Evo_Whisper100_40SPD_LITDDA_HeLa_5ng_Turbo_1CV_8ms_S01") %>% 
  pull(Sequence)

DDA_5_2_pep <- DDA_5 %>% 
  filter(`Raw file` ==
           "20220414_HB_Evo_Whisper100_40SPD_LITDDA_HeLa_5ng_Turbo_1CV_8ms_S02") %>% 
  pull(Sequence)

DDA_5_3_pep <- DDA_5 %>% 
  filter(`Raw file` ==
           "20220414_HB_Evo_Whisper100_40SPD_LITDDA_HeLa_5ng_Turbo_1CV_8ms_S03") %>% 
  pull(Sequence)

DDA_5_4_pep <- DDA_5 %>% 
  filter(`Raw file` ==
           "20220414_HB_Evo_Whisper100_40SPD_LITDDA_HeLa_5ng_Turbo_1CV_8ms_S04") %>% 
  pull(Sequence)
```


DDA 10ng
```{r}
table(DDA_10$`Raw file`)

DDA_10_1_pep <- DDA_10 %>% 
  filter(`Raw file` ==
           "20220414_HB_Evo_Whisper100_40SPD_LITDDA_HeLa_10ng_Turbo_1CV_8ms_S01") %>% 
  pull(Sequence)

DDA_10_2_pep <- DDA_10 %>% 
  filter(`Raw file` ==
           "20220414_HB_Evo_Whisper100_40SPD_LITDDA_HeLa_10ng_Turbo_1CV_8ms_S02") %>% 
  pull(Sequence)

DDA_10_3_pep <- DDA_10 %>% 
  filter(`Raw file` ==
           "20220414_HB_Evo_Whisper100_40SPD_LITDDA_HeLa_10ng_Turbo_1CV_8ms_S03") %>% 
  pull(Sequence)

DDA_10_4_pep <- DDA_10 %>% 
  filter(`Raw file` ==
           "20220414_HB_Evo_Whisper100_40SPD_LITDDA_HeLa_10ng_Turbo_1CV_8ms_S04") %>% 
  pull(Sequence)
```


DDA 100ng
```{r}
table(DDA_100$`Raw file`)

DDA_100_1_pep <- DDA_100 %>% 
  filter(`Raw file` ==
           "20220413_HB_Evo_Whisper100_40SPD_LITDDA_HeLa_100ng_Turbo_1CV_8ms_S01") %>% 
  pull(Sequence)

DDA_100_2_pep <- DDA_100 %>% 
  filter(`Raw file` ==
           "20220413_HB_Evo_Whisper100_40SPD_LITDDA_HeLa_100ng_Turbo_1CV_8ms_S02") %>% 
  pull(Sequence)

DDA_100_3_pep <- DDA_100 %>% 
  filter(`Raw file` ==
           "20220413_HB_Evo_Whisper100_40SPD_LITDDA_HeLa_100ng_Turbo_1CV_8ms_S03") %>% 
  pull(Sequence)

DDA_100_4_pep <- DDA_100 %>% 
  filter(`Raw file` ==
           "20220413_HB_Evo_Whisper100_40SPD_LITDDA_HeLa_100ng_Turbo_1CV_8ms_S04") %>% 
  pull(Sequence)
```

DIA 1ng
```{r}
DIA_1 <- DIA_1 %>% 
  filter(EG.IsImputed == "False")

table(DIA_1$R.FileName)

DIA_1_1_pep <- DIA_1 %>% 
  filter(R.FileName ==
           "20220221_EV_Evo_Whisper100_40SPD_HeLa_1ng_1CV45_LITDIA_Turbo_8ms_s01") %>% 
  pull(PEP.StrippedSequence)

DIA_1_2_pep <- DIA_1 %>% 
  filter(R.FileName ==
           "20220221_EV_Evo_Whisper100_40SPD_HeLa_1ng_1CV45_LITDIA_Turbo_8ms_s02") %>% 
  pull(PEP.StrippedSequence)

DIA_1_3_pep <- DIA_1 %>% 
  filter(R.FileName ==
           "20220221_EV_Evo_Whisper100_40SPD_HeLa_1ng_1CV45_LITDIA_Turbo_8ms_s03") %>% 
  pull(PEP.StrippedSequence)

DIA_1_4_pep <- DIA_1 %>% 
  filter(R.FileName ==
           "20220221_EV_Evo_Whisper100_40SPD_HeLa_1ng_1CV45_LITDIA_Turbo_8ms_s04") %>% 
  pull(PEP.StrippedSequence)
```


DIA 5ng
```{r}
DIA_5 <- DIA_5 %>% 
  filter(EG.IsImputed == "False")

table(DIA_5$R.FileName)

DIA_5_1_pep <- DIA_5 %>% 
  filter(R.FileName ==
           "20220221_EV_Evo_Whisper100_40SPD_HeLa_5ng_1CV45_LITDIA_Turbo_8ms_s01") %>% 
  pull(PEP.StrippedSequence)

DIA_5_2_pep <- DIA_5 %>% 
  filter(R.FileName ==
           "20220221_EV_Evo_Whisper100_40SPD_HeLa_5ng_1CV45_LITDIA_Turbo_8ms_s02") %>% 
  pull(PEP.StrippedSequence)

DIA_5_3_pep <- DIA_5 %>% 
  filter(R.FileName ==
           "20220221_EV_Evo_Whisper100_40SPD_HeLa_5ng_1CV45_LITDIA_Turbo_8ms_s03") %>% 
  pull(PEP.StrippedSequence)

DIA_5_4_pep <- DIA_5 %>% 
  filter(R.FileName ==
           "20220221_EV_Evo_Whisper100_40SPD_HeLa_5ng_1CV45_LITDIA_Turbo_8ms_s04") %>% 
  pull(PEP.StrippedSequence)
```

DIA 10ng
```{r}

DIA_10 <- DIA_10 %>% 
  filter(EG.IsImputed == "False")

table(DIA_10$R.FileName)

DIA_10_1_pep <- DIA_10 %>% 
  filter(R.FileName ==
           "20220221_EV_Evo_Whisper100_40SPD_HeLa_10ng_1CV45_LITDIA_Turbo_8ms_s01") %>% 
  pull(PEP.StrippedSequence)

DIA_10_2_pep <- DIA_10 %>% 
  filter(R.FileName ==
           "20220221_EV_Evo_Whisper100_40SPD_HeLa_10ng_1CV45_LITDIA_Turbo_8ms_s02") %>% 
  pull(PEP.StrippedSequence)

DIA_10_3_pep <- DIA_10 %>% 
  filter(R.FileName ==
           "20220221_EV_Evo_Whisper100_40SPD_HeLa_10ng_1CV45_LITDIA_Turbo_8ms_s03") %>% 
  pull(PEP.StrippedSequence)

DIA_10_4_pep <- DIA_10 %>% 
  filter(R.FileName ==
           "20220221_EV_Evo_Whisper100_40SPD_HeLa_10ng_1CV45_LITDIA_Turbo_8ms_s04") %>% 
  pull(PEP.StrippedSequence)
```

DIA 100ng
```{r}

DIA_100 <- DIA_100 %>% 
  filter(EG.IsImputed == "False")

table(DIA_100$R.FileName)

DIA_100_1_pep <- DIA_100 %>% 
  filter(R.FileName ==
           "20220412_HB_Evo_Whisper100_40SPD_LITDIA_HeLa_100ng_Turbo_1CV_8ms_S01") %>% 
  pull(PEP.StrippedSequence)

DIA_100_2_pep <- DIA_100 %>% 
  filter(R.FileName ==
           "20220412_HB_Evo_Whisper100_40SPD_LITDIA_HeLa_100ng_Turbo_1CV_8ms_S02") %>% 
  pull(PEP.StrippedSequence)

DIA_100_3_pep <- DIA_100 %>% 
  filter(R.FileName ==
           "20220412_HB_Evo_Whisper100_40SPD_LITDIA_HeLa_100ng_Turbo_1CV_8ms_S03") %>% 
  pull(PEP.StrippedSequence)

DIA_100_4_pep <- DIA_100 %>% 
  filter(R.FileName ==
           "20220412_HB_Evo_Whisper100_40SPD_LITDIA_HeLa_100ng_Turbo_1CV_8ms_S04") %>% 
  pull(PEP.StrippedSequence)
```

#### Remove peptides found in only one replicate

DDA 1ng
```{r}
DDA_1 <- DDA_1 %>% 
  mutate(in_1 = Sequence %in% DDA_1_1_pep) %>% 
  mutate(in_2 = Sequence %in% DDA_1_2_pep) %>% 
  mutate(in_3 = Sequence %in% DDA_1_3_pep) %>% 
  mutate(in_4 = Sequence %in% DDA_1_4_pep)

DDA_1_filtered <- DDA_1 %>% 
  filter(rowSums(DDA_1[, 63:66]) >= 2)
```

DDA 5ng
```{r}
DDA_5 <- DDA_5 %>% 
  mutate(in_1 = Sequence %in% DDA_5_1_pep) %>% 
  mutate(in_2 = Sequence %in% DDA_5_2_pep) %>% 
  mutate(in_3 = Sequence %in% DDA_5_3_pep) %>% 
  mutate(in_4 = Sequence %in% DDA_5_4_pep)

DDA_5_filtered <- DDA_5 %>% 
  filter(rowSums(DDA_5[, 63:66]) >= 2)
```

DDA 10ng
```{r}
DDA_10 <- DDA_10 %>% 
  mutate(in_1 = Sequence %in% DDA_10_1_pep) %>% 
  mutate(in_2 = Sequence %in% DDA_10_2_pep) %>% 
  mutate(in_3 = Sequence %in% DDA_10_3_pep) %>% 
  mutate(in_4 = Sequence %in% DDA_10_4_pep)

DDA_10_filtered <- DDA_10 %>% 
  filter(rowSums(DDA_10[, 63:66]) >= 2)
```

DDA 100ng
```{r}
DDA_100 <- DDA_100 %>% 
  mutate(in_1 = Sequence %in% DDA_100_1_pep) %>% 
  mutate(in_2 = Sequence %in% DDA_100_2_pep) %>% 
  mutate(in_3 = Sequence %in% DDA_100_3_pep) %>% 
  mutate(in_4 = Sequence %in% DDA_100_4_pep)

DDA_100_filtered <- DDA_100 %>% 
  filter(rowSums(DDA_100[, 63:66]) >= 2)
```

DIA 1ng
```{r}
DIA_1 <- DIA_1 %>% 
  mutate(in_1 = PEP.StrippedSequence %in% DIA_1_1_pep) %>% 
  mutate(in_2 = PEP.StrippedSequence %in% DIA_1_2_pep) %>% 
  mutate(in_3 = PEP.StrippedSequence %in% DIA_1_3_pep) %>% 
  mutate(in_4 = PEP.StrippedSequence %in% DIA_1_4_pep)

DIA_1_filtered <- DIA_1 %>% 
  filter(rowSums(DIA_1[, 55:58]) >= 2)
```

DIA 5ng
```{r}
DIA_5 <- DIA_5 %>% 
  mutate(in_1 = PEP.StrippedSequence %in% DIA_5_1_pep) %>% 
  mutate(in_2 = PEP.StrippedSequence %in% DIA_5_2_pep) %>% 
  mutate(in_3 = PEP.StrippedSequence %in% DIA_5_3_pep) %>% 
  mutate(in_4 = PEP.StrippedSequence %in% DIA_5_4_pep)

DIA_5_filtered <- DIA_5 %>% 
  filter(rowSums(DIA_5[, 55:58]) >= 2)
```

DIA 10ng
```{r}
DIA_10 <- DIA_10 %>% 
  mutate(in_1 = PEP.StrippedSequence %in% DIA_10_1_pep) %>% 
  mutate(in_2 = PEP.StrippedSequence %in% DIA_10_2_pep) %>% 
  mutate(in_3 = PEP.StrippedSequence %in% DIA_10_3_pep) %>% 
  mutate(in_4 = PEP.StrippedSequence %in% DIA_10_4_pep)

DIA_10_filtered <- DIA_10 %>% 
  filter(rowSums(DIA_10[, 55:58]) >= 2)
```

DIA 100ng
```{r}
DIA_100 <- DIA_100 %>% 
  mutate(in_1 = PEP.StrippedSequence %in% DIA_100_1_pep) %>% 
  mutate(in_2 = PEP.StrippedSequence %in% DIA_100_2_pep) %>% 
  mutate(in_3 = PEP.StrippedSequence %in% DIA_100_3_pep) %>% 
  mutate(in_4 = PEP.StrippedSequence %in% DIA_100_4_pep)

DIA_100_filtered <- DIA_100 %>% 
  filter(rowSums(DIA_100[, 55:58]) >= 2)
```

## UpSet plot

```{r}
pep_list <- 
  list('DDA 1ng' = unique(DDA_1_filtered$Sequence),
       'DDA 5ng' = unique(DDA_5_filtered$Sequence),
       'DDA 10ng' = unique(DDA_10_filtered$Sequence),
       'DDA 100ng' = unique(DDA_100_filtered$Sequence),
       'DIA 1ng' = unique(DIA_1_filtered$PEP.StrippedSequence),
       'DIA 5ng' = unique(DIA_5_filtered$PEP.StrippedSequence),
       'DIA 10ng' = unique(DIA_10_filtered$PEP.StrippedSequence),
       'DIA 100ng' = unique(DIA_100_filtered$PEP.StrippedSequence))

palette <- c("pink3", "pink2", "pink1", "pink",
             "steelblue", "steelblue3", "steelblue2", "steelblue1")

upset(fromList(pep_list),
      sets = c('DIA 100ng', 'DIA 10ng', 'DIA 5ng', 'DIA 1ng',
               'DDA 100ng', 'DDA 10ng', 'DDA 5ng', 'DDA 1ng'),
      order.by = "freq", 
      keep.order = TRUE,
      set_size.show = TRUE, 
      sets.bar.color = palette,
      mainbar.y.label = "Number of identified peptides",
      nsets = 8,
      text.scale = 1.1)
```

# CV

## Load dataset

LITDIA turbo
```{r}

turbo_1 <- 
  read.csv2(paste0(path, "CVs/Peptide_CVs_LITDIA_turbo_1ng.tsv"),
           sep = "\t")
turbo_5 <- 
  read.csv2(paste0(path, "CVs/Peptide_CVs_LITDIA_turbo_5ng.tsv"),
           sep = "\t")
turbo_10 <- 
  read.csv2(paste0(path, "CVs/Peptide_CVs_LITDIA_turbo_10ng.tsv"),
           sep = "\t")
turbo_100 <- 
  read.csv2(paste0(path, "CVs/Peptide_CVs_LITDIA_turbo_100ng.tsv"),
           sep = "\t")

```

LITDIA normal
```{r}
normal_1 <- 
  read.csv2(paste0(path, "CVs/Peptide_CVs_LITDIA_normal_1ng.tsv"),
           sep = "\t")
normal_5 <- 
  read.csv2(paste0(path, "CVs/Peptide_CVs_LITDIA_normal_5ng.tsv"),
           sep = "\t")
normal_10 <- 
  read.csv2(paste0(path, "CVs/Peptide_CVs_LITDIA_normal_10ng.tsv"),
           sep = "\t")
normal_100 <- 
  read.csv2(paste0(path, "CVs/Peptide_CVs_LITDIA_normal_100ng.tsv"),
           sep = "\t")
```


OT 7.5k
```{r}
OT_7.5k_1 <- 
  read.csv2(paste0(path, "CVs/Peptide_CVs_OT_7.5k_1ng.tsv"),
            sep = "\t")
OT_7.5k_5 <- 
  read.csv2(paste0(path, "CVs/Peptide_CVs_OT_7.5k_5ng.tsv"),
           sep = "\t")
OT_7.5k_10 <- 
  read.csv2(paste0(path, "CVs/Peptide_CVs_OT_7.5k_10ng.tsv"),
           sep = "\t")
OT_7.5k_100 <- 
  read.csv2(paste0(path, "CVs/Peptide_CVs_OT_7.5k_100ng.tsv"),
           sep = "\t")
```

OT 15k
```{r}
OT_15k_1 <- 
  read.csv2(paste0(path, "CVs/Peptide_CVs_OT_15k_1ng.tsv"),
           sep = "\t")
OT_15k_5 <- 
  read.csv2(paste0(path, "CVs/Peptide_CVs_OT_15k_5ng.tsv"),
           sep = "\t")
OT_15k_10 <- 
  read.csv2(paste0(path, "CVs/Peptide_CVs_OT_15k_10_ng.tsv"),
           sep = "\t")
OT_15k_100 <- 
  read.csv2(paste0(path, "CVs/Peptide_CVs_OT_15k_100ng.tsv"),
           sep = "\t")
```

## join table

```{r}
colnames(turbo_1) <- colnames(turbo_5) <-  colnames(turbo_10) <- colnames(turbo_100) <- 
  colnames(normal_1) <- colnames(normal_5) <- colnames(normal_10) <- colnames(normal_100) <- 
  colnames(OT_7.5k_1) <- colnames(OT_7.5k_5) <- colnames(OT_7.5k_10) <- colnames(OT_7.5k_100) <-
  colnames(OT_15k_1) <- colnames(OT_15k_5) <- colnames(OT_15k_10) <- colnames(OT_15k_100) <- "CV"
```


LITDIA
```{r}
turbo_1$ng <- 1
turbo_5$ng <- 5
turbo_10$ng <- 10
turbo_100$ng <- 100

turbo <- rbind(turbo_1, turbo_5, turbo_10, turbo_100)

turbo$method <- "LITDIA_turbo"
```

Normal
```{r}
normal_1$ng <- 1
normal_5$ng <- 5
normal_10$ng <- 10
normal_100$ng <- 100

normal <- rbind(normal_1, normal_5, normal_10, normal_100)

normal$method <- "LITDIA_normal"
```

OT 7.5k
```{r}
OT_7.5k_1$ng <- 1
OT_7.5k_5$ng <- 5
OT_7.5k_10$ng <- 10
OT_7.5k_100$ng <- 100

OT_7.5k <- rbind(OT_7.5k_1, OT_7.5k_5, OT_7.5k_10, OT_7.5k_100)

OT_7.5k$method <- "OT_7.5k"
```

OT 15k
```{r}
OT_15k_1$ng <- 1
OT_15k_5$ng <- 5
OT_15k_10$ng <- 10
OT_15k_100$ng <- 100

OT_15k <- rbind(OT_15k_1, OT_15k_5, OT_15k_10, OT_15k_100)

OT_15k$method <- "OT_15k"
```

## boxplot

```{r}
teera_palette <- c(rep(c("#C9D7F0", "#7F9FDB", "#527DCE", "#ADC2E8"),2),
                   rep(c("#EEB9CF", "#DF7FA7","#D35087",  "#EAACC6"),2))

combined <- rbind(turbo, normal, OT_15k, OT_7.5k)
combined$condition <- paste(combined$method, combined$ng, sep = "_")
combined$method <- factor(combined$method, 
                          levels = c("LITDIA_turbo", "LITDIA_normal", 
                                     "OT_7.5k", "OT_15k"))

combined %>% 
  ggplot(aes(x = as.factor(ng), y = CV, fill = as.factor(condition)))+
  geom_boxplot(outlier.size = 0.7)+
  theme_bw()+
  scale_fill_manual(values = teera_palette)+
  scale_y_log10(breaks = c(1, 10, 20, 100),
                limits = c(0.2, 195))+
  geom_hline(yintercept = 20,
             linetype = "dashed")+
  labs(x = "Protein Amount (ng)",
       y = "CV (%)",
       title = "CV Distribution")+
  theme(legend.position = "none",
        plot.title = element_text(hjust = 0.5))+
  facet_wrap(~method, labeller = labeller(method = 
    c("LITDIA_turbo" = "LITDIA Turbo",
      "LITDIA_normal" = "LITDIA Normal",
      "OT_15k" = "OT 15k",
      "OT_7.5k" = "OT 7.5k")))
```

```{r, include=FALSE}
DIA_1_intensity <- DIA_1_filtered %>% 
  group_by(PEP.StrippedSequence) %>% 
  summarise(mean_quantity = mean(FG.Quantity))

DDA_1_intensity <- DDA_1_filtered %>% 
  group_by(Sequence) %>% 
  summarise(mean_intensity = mean(Intensity))

join <- inner_join(DIA_1_intensity, 
           DDA_1_intensity, 
           by = c("PEP.StrippedSequence" = "Sequence"))

ggscatter(data = join,
          x = "mean_quantity",
          y = "mean_intensity",
          add = "reg.line",
          add.params = list(color = "red"), 
          color = "grey25")+
  stat_cor(method = "pearson",
           aes(label = ..r.label..),
           r.digits = 3, color = "red")+
  scale_x_log10()+
  scale_y_log10()+
  labs(x = "DIA Abundance (log10)",
       y = "DDA Abundance (log10)")
```

```{r, include=FALSE}
DIA_10_intensity <- DIA_10_filtered %>% 
  group_by(PEP.StrippedSequence) %>% 
  summarise(mean_quantity = mean(FG.Quantity))

DDA_10_intensity <- DDA_10_filtered %>% 
  group_by(Sequence) %>% 
  summarise(mean_intensity = mean(Intensity))

join <- inner_join(DIA_10_intensity, 
           DDA_10_intensity, 
           by = c("PEP.StrippedSequence" = "Sequence"))

ggscatter(data = join,
          x = "mean_quantity",
          y = "mean_intensity",
          add = "reg.line",
          add.params = list(color = "red"), 
          color = "grey25")+
  stat_cor(method = "pearson",
           aes(label = ..r.label..),
           r.digits = 3, color = "red")+
  scale_x_log10()+
  scale_y_log10()+
  labs(x = "DIA Abundance (log10)",
       y = "DDA Abundance (log10)")
```
```{r, include=FALSE}
DIA_100_intensity <- DIA_100_filtered %>% 
  group_by(PEP.StrippedSequence) %>% 
  summarise(mean_quantity = mean(FG.Quantity))

DDA_100_intensity <- DDA_100_filtered %>% 
  group_by(Sequence) %>% 
  summarise(mean_intensity = mean(Intensity))

join <- inner_join(DIA_100_intensity, 
           DDA_100_intensity, 
           by = c("PEP.StrippedSequence" = "Sequence"))

ggscatter(data = join,
          x = "mean_quantity",
          y = "mean_intensity",
          add = "reg.line",
          add.params = list(color = "red"), 
          color = "grey25")+
  stat_cor(method = "pearson",
           aes(label = ..r.label..),
           r.digits = 3, color = "red")+
  scale_x_log10()+
  scale_y_log10()+
  labs(x = "DIA Abundance (log10)",
       y = "DDA Abundance (log10)")
```
